Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-01-03 doc_v2/doc_v2.Rmd
.

```{r }

#knitr::kable(a27, digits=0, caption = "Window of Optimization 320 and Window of Validation 50", format = "latex" ,booktabs=TRUE)%>% kableExtra::kable_styling(latex_options = c("hold"))

```{r}

#knitr::kable(a27, digits=0, caption = "Window of Optimization 120 and Window of Validation 50", format = "latex" ,booktabs=TRUE)%>% kableExtra::kable_styling(latex_options = c("hold"))
```

```{r param, echo=FALSE, results='asis'}
param_setting<- all %>% select(wo, wv) %>% group_by(wo, wv) %>% tally() %>% select(wo,wv)
#param_setting<- data.frame(matrix(param_setting, nrow = 16))
#t(param_setting)
#param_setting %>% tally() 
library(kableExtra)
#knitr::kable(t(param_setting)[,1:17], digits=0, caption = "Overview of parameter settings used for optimization and validation windows for bullet land signatures.", format = "latex" ,booktabs=TRUE) %>% kableExtra::kable_styling(latex_options = c("scale_down", "hold"))

@@

# Results

We used the adjusted Chumbley method as proposed in \citet{hadler} and implemented in the R package `toolmaRk` \citep{toolmark} on all pairwise land-to-land comparisons of the Hamby scans (a total of 85,491 comparisons) with the pairwise sets for the comparisons given in the table \ref{tab:param}.

>>>>

# Results
We used the adjusted Chumbley method as proposed in \citet{hadler} and implemented in the R package `toolmaRk` \citep{toolmark} on all pairwise land-to-land comparisons of the Hamby scans (a total of 85,491 comparisons) with the pairwise sets for the comparisons given in the table \ref{tab:param}.
```{r param}
param_setting<- all %>% select(wo, wv) %>% group_by(wo, wv) %>% tally() %>% select(wo,wv)
#param_setting<- data.frame(matrix(param_setting, nrow = 16))
#t(param_setting)
#param_setting %>% tally() 
library(kableExtra)
#knitr::kable(t(param_setting)[,1:17], digits=0, caption = "Overview of parameter settings used for optimization and validation windows for bullet land signatures.", format = "latex" ,booktabs=TRUE) %>% kableExtra::kable_styling(latex_options = c("scale_down", "hold"))

@@
